Robust Adaptation to Multi-Scale Climate Variability

### 2019-01-10 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
add two more references

We finally consider a model which explicitly represents \acrlong{lfv}.
A \gls{hmm} is a latent variable model in which the system being modeled is assumed to follow a Markov process with unobserved (\ie hidden) states $S(t)$ \citep{Rabiner:1986jk}.
The (unobserved) states evolve following a first-order Markov process, and the observed variable (\eg streamflow) depends only on the underlying state.
We fit  streamflow sequences $Q_\text{hist}$ simulated using the scenarios in Section 2.1, using a \gls{hmm} with two states.
The model is fit using the Baum-Welch algorithm, assuming that the data follow a log-normal distribution conditional only on the state.
This algorithm simultaneously estimates the transition matrix of the Markov process and the conditional parameters of each distribution.
For simplicity, we fit only a two-state \gls{hmm} to each sequence.
Future floods are then estimated by simulating future states from the estimated transition matrix and then drawing $Q(t)$ conditional on the simulated state.

>>>>

We finally consider a model which explicitly represents \acrlong{lfv}.
A \gls{hmm} is a latent variable model in which the system being modeled is assumed to follow a Markov process with unobserved (\ie hidden) states $S(t)$ \citep{Rabiner:1986jk}.
The (unobserved) states evolve following a first-order Markov process, and the observed variable (\eg streamflow) depends only on the underlying state.
\Glspl{hmm} have been widely used for modeling streamflow sequences \citep{Bracken:2016ba} and \gls{enso} \citep{rojohernandez:2017}.
We fit  streamflow sequences using a \gls{hmm} with two states.
The model is fit using the Baum-Welch algorithm, assuming that the data follow a log-normal distribution conditional only on the state.
This algorithm simultaneously estimates the transition matrix of the Markov process and the conditional parameters of each distribution.
For simplicity, we fit only a two-state \gls{hmm} to each sequence.
Future floods are then estimated by simulating future states from the estimated transition matrix and then drawing $Q(t)$ conditional on the simulated state.
